Interval-Valued Quantum Probabilities: Contextuality and the Born Rule

### 2017-05-13 prop_letter.tex
restructure a bit
question

@@

@@

\begin{definition}
$\bar{\mu}$ is called convex if for all commuting $P_{0},P_{1}\in\events$,
$\bar{\mu}\left(P_{0}\vee P_{1}\right)+\bar{\mu}\left(P_{0}P_{1}\right)\subseteq\bar{\mu}\left(P_{0}\right)+\bar{\mu}\left(P_{1}\right)$,
where $P_{0}\vee P_{1}=P_{0}+P_{1}-P_{0}P_{1}$ \cite{Griffiths2003}.
\end{definition}

@@

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Quantum States}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Convexity}

In the classical setting, IVPMs typically are equipped with additional
conditions to ensure they are ``well-behaved.''

Yu-Tsung: please construct an example with commuting events P0 and P1 such that:

mu(P0 + P1 - P0P1) + mu(P0P1) = [x,y]
mu(P0) + mu(P1) = [z,w]

and [x,y] is NOT included in [z,w]

@@

Not specific to quantum; fuziness also in classical setting

@@

\begin{definition}
$\bar{\mu}$ is called convex~\cite{Griffiths2003}. if for all
commuting $P_{0},P_{1}\in\events$, we have
$\bar{\mu}\left(P_{0}+P_{1}-P_{0}P_{1}\right)+\bar{\mu}\left(P_{0}P_{1}\right)\subseteq\bar{\mu}\left(P_{0}\right)+\bar{\mu}\left(P_{1}\right)$.
\end{definition}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Fuzzy Observables}

@@
